---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hitac2

Warning: This package is still under development and lacks proper documentation / help / testing!

__very, very BAAAAD!__

For a first glimpse, check this out!

## Installation

You can install the released version of hitac2 from GitHub.

```{r installation, eval = FALSE}
# should not work, since the repo is private
# devtools::install_github("mirkko-hub/hitac2")
```

```{r}
library(tidyverse, warn.conflicts = FALSE)
library(magrittr, warn.conflicts = FALSE)
library(hitac2)
library(minpack.lm)
```

### Example workflow

* read data

```{r read_data}
ha_data <- hitachi_read(system.file("extdata", "D0X00000.001", package = "hitac2", mustWork = TRUE))
design <- read_csv(system.file("extdata", "design.csv", package = "hitac2", mustWork = TRUE))
treatment <- read_csv(system.file("extdata", "treatment.csv", package = "hitac2", mustWork = TRUE))

ha_data <- left_join(ha_data, design, by = "Hitachi_ID")
```

* calculate specific activity (sa) and do background subtraction (bg)
*  _how many CPM per given amount of NaHCO3?_

```{r calculate_sa}
table_activity <- hitachi_tibble(data = ha_data, treatment = treatment, V_RuBP = 4e-06, C_RuBP = 6e-04, convert = TRUE)
```

* quick check of control samples (sa and bg)

```{r plot_control, echo=FALSE}
# especially interesting for multiple replicates, here only one is shown
ggplot(data = ha_data %>% filter(Group %in% c("sa", "bg")),
                   mapping = aes(x = Set_ID, y = CPM)) +
  geom_boxplot(aes(group = Set_ID)) +
  geom_point(aes(group = Set_ID)) +
  # facet_grid(Groups ~ .)
  facet_wrap("Group", scales = "free")
```
* quick check of actual data

```{r plot_data, echo=FALSE}
data_dosedependence <- filter(table_activity, Group %in% LETTERS[7:12]) 
data_dosedependence %>%
  mutate(Time_min = Time_s / 60) %>%
  ggplot(., mapping = aes(x = Time_min, y = Activity_nmol, colour = Label)) +
  geom_smooth(mapping = aes(colour = Label), linetype = 3, size = 0.6, se = F) +
  # geom_point(mapping = aes(colour = Label)) +
  geom_pointrange(data = data_dosedependence %>%
                    mutate(Time_min = Time_s / 60) %>% 
                    group_by(Label, Time_min) %>%
                    summarise(Activity_avg = mean(Activity_nmol), Activity_sd = sd(Activity_nmol)) %>%
                    mutate(Activity_nmol = Activity_avg),
                  mapping = aes(x = Time_min, ymin = Activity_avg - Activity_sd, ymax = Activity_avg + Activity_sd, colour = Label),
                  fatten = 0.2) +
   labs(x = expression(paste("Time (min)")), y = expression(paste("fixed carbon (" ,nmol, ")")))

```

### Add some models

* fit an inappropriate model and plot for visualization

```{r model}
# model
sigmoidal_nls_4p <- function(df){
  `minpack.lm`::nlsLM(Activity_nmol ~ asym_high + ((asym_low - asym_high) / (1+exp(slope * (Time_min - Time_inflect)))),
      data = df,
      start = list(asym_low = min(df$Activity_nmol),
                   asym_high = max(df$Activity_nmol),
                   slope = 1,
                   Time_inflect = max(df$Time_min) / 2))
}

# fit
data_dosedependence %>%
  mutate(Time_min = Time_s / 60) %>%
  select(Label, Time_min, Activity_nmol) %>%
  nest(data = c(Time_min, Activity_nmol)) %>%
  mutate(model = map(data, sigmoidal_nls_4p)) %>% select(Label, model) %>%
  right_join(tibble(
    Label = rep(.$Label %>% unique, each = 49),
    Time_min = rep(seq(2, 26, by = 0.5), 6)),
    by = "Label") %>%
  nest(data = c(Time_min)) %>%
  mutate(`Activity fitted` = map2(data, model, modelr::add_predictions, var = "Activity fitted")) %>%
  unnest(`Activity fitted`) %>%
  ggplot(.) +
  geom_line(aes(x = Time_min, y = `Activity fitted`, colour = Label)) +
  # for multiple replicates
  geom_pointrange(data = data_dosedependence %>%
                    mutate(Time_min = Time_s / 60) %>%
                    group_by(Label, Time_min) %>%
                    summarise(Activity_avg = mean(Activity_nmol), Activity_sd = sd(Activity_nmol)),
                  mapping = aes(x = Time_min, y = Activity_avg,
                                ymin = Activity_avg - Activity_sd,
                                ymax = Activity_avg + Activity_sd, colour = Label),
                  fatten = 0.2) +
  labs(x = expression(paste("Time (min)")), y = expression(CO[2] ~ (nmol)))

```

* how about a michaelis-menten plot?

```{r michaelis_menten}
# some more data
michaelis_menten

# fit groupwise (1 per Concentration), linear models
ha_extract_lm <- hitachi_extract_lm(data = michaelis_menten) # raw-data for plotting linear models

# extract estimates of linear model
ha_extract_rate <- hitachi_extract_rate(ha_extract_lm)

# build model matrix
ha_modelmatrix <- hitachi_model(ha_extract_rate)

# plot
ggplot(ha_extract_rate, aes(x = S, y = v)) +
  theme_bw() +
  labs(y = expression(paste("initial velocity ( ", nmol / sec, " )")), x = expression(paste("[RuBP] ( ", mM, " )"))) +
  geom_point(size = 0.5) +
  geom_errorbar(data = ha_extract_rate, aes(x = S, ymin = v - std.error, ymax = v + std.error)) +
  geom_line(data = ha_modelmatrix, aes(x = S, y = Velocity_mod, colour = model))

```


